Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/concl.tex
do not mention the url due to anonymous submission
done with a pass

This paper presented the initial design and implementation of
\textit{Nail}, an interface generator for data formats.  Nail helps
programmers to avoid memory corruption and ambiguity vulnerabilities
while reducing effort in parsing and generating real-world protocols
and file formats.  Nail achieves this by reducing the expressive
power of the grammar, maintaining a \emph{semantic bijection} between
data formats and internal representations, and allowing programmers to
specify \emph{structural dependencies} in the data format.  Preliminary
experience with implementing a DNS server using Nail suggests that this
is a promising approach.

The source code for our prototype of Nail is available at
\url{https://github.com/jbangert/nail}.

>>>>

This paper presented the design and implementation of \textit{Nail},
an interface generator for data formats.  Nail helps programmers avoid
memory corruption and ambiguity vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
maintaining a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.

% The source code for our prototype of Nail is available at
% \url{https://github.com/jbangert/nail}.

### 2014-05-01 paper/osdi14/eval.tex
done with a pass

To estimate the performance impact of using Nail grammars as opposed to hand-written grammars, we
benchmarked our DNS server against BIND.

@@

We compare the performance of our DNS server to the release 9.9.5 of ISC BIND 9\cite{bind9}, one of
the oldest and most popular DNS daemons, on a load that resembles the authoritative name server at a
hosting company. First, we generated domain names consisting of one or
two labels randomly selected from an English dictionary and one label that is one of three popular
Top Level Domains: ``com'', ``net'' or ``org''. Second, we randomly selected 90\% of these domains and
created a zone file that mapped these domain names to the local IP address.

Finally, we used the \cc{queryperf} tool provided with BIND to query each domain between zero
and three times on a local instance of BIND or NailDNS. Both DNS servers were operating on a single, 
core  of an Intel i7-3610QM with 12GB of RAM on an idle system, and the benchmark tool kept at most 20
queries outstanding at once. The queryperf tool was configured to
repeat the same, randomized sequence of queries for one minute and the average throughput and
response latency were measured.  We repeated each test seven times  with 50.000
domain names, restarting each daemon in between. We also performed one initial dry run to warm the
file system cache for the zone file. We repeated the tests with 1 million domain names and found
that the servers performed almost identically.

Surprisingly, our simple Nail server outperforms the established BIND server that has seen decades
of optimization by a factor of 3.  This demonstrates that even though Nail was
not developed focusing on performance, applications built on Nail can compete with real-world
hand-written parsers.

>>>>

To evaluate whether Nail-based parsers are compatible with good
performance, we compare the performance of our DNS server to that of ISC
BIND 9 release 9.9.5~\cite{bind9}, a mature and widely used DNS server.
We simulate a load resembling that of an authoritative name server.
First, we generate domain names consisting of one or two labels randomly
selected from an English dictionary, and one label that is one of
three popular top-level domains (\cc{com}, \cc{net}, and \cc{org}).
Second, we randomly selected 90\% of these domains and created a zone
file that mapped these domain names to \cc{127.0.0.1}.  Finally, we used
the \cc{queryperf} tool provided with BIND to query each domain between
zero and three times, using a DNS server running on the local machine.
We used a single core of an Intel i7-3610QM system with 12GB of RAM.
The benchmark tool kept at most 20 queries outstanding at once, and
was configured to repeat the same randomized sequence of queries for
one minute.  We repeated each test seven times with 50,000 domain names,
restarting each daemon in between; we also repeated the tests with 1
million domain names, and found similar results.  We also performed one
initial dry run to warm the file system cache for the zone file.

The results are shown in Figure~\ref{fig:perf-dns}, and demonstrate that
our Nail-based DNS server can achieve higher performance and lower latency
than BIND\@.  Although BIND is a much more sophisticated DNS server,
and implements many features that are not present in our Nail-based DNS
server, we believe our results demonstrate that Nail's parsers are not
a barrier to achieving acceptable performance.

@@

### 2014-05-01 paper/osdi14/future.tex
Initial syntax table
done with a pass

The Nail parser generator is currently a work-in-progress, and we would
appreciate feedback on our initial design and prototype implementation.
Short-term next steps include improving the scoping of dependency fields
and adding support for offset fields.

@@

Finally, we would like to demonstrate the capabilities of Nail by
implementing various binary formats ``notorious'' for their insecurity
in Nail. Nail was designed with the idioms of formats such as PDF and
PNG in mind. Ultimately, we want to provide examples of successful Nail
parsers throughout a network stack, from a user-space TCP stack to a
PNG de-compressor.

>>>>

@@

% Finally, we would like to demonstrate the capabilities of Nail by
% implementing various binary formats ``notorious'' for their insecurity
% in Nail. Nail was designed with the idioms of formats such as PDF and
% PNG in mind. Ultimately, we want to provide examples of successful Nail
% parsers throughout a network stack, from a user-space TCP stack to a
% PNG de-compressor.
